Catchy Title

### 2011-10-11 proposal/paper.tex
Adding more refs

SPIRIT \cite{papadimitriou2005streaming} is an algorithm for discovering patterns in multiple streams of time-series data. This algorithm effectively tries to find correlations between the different data streams by performing principal component analysis on the the data covariance matrix. These principal components are modified and updated as each data sample is received at each time step while forgetting the samples. An interesting aspect of this algorithm is, anomaly detection which is done by detecting the changes in the number of principal components required to capture most of the energy in the signal.
In \cite{roweis1999unifying} the authors describe a unifying model for Linear Gaussian Models which includes PCA, Kalman Filters, Gaussian Mixture Models, ICA etc. They describe a general linear state transition model along with a linear observation model corrupted by independent Gaussian noise. They describe general algorithms to do inference and also learn the parameters of the model.

@@

Another console logs mining paper \cite{xu2009} extracts specific features from unstructured logs of Hadoop system \cite{Hadoop} (A distributed system for data intensive computing) and use them to detect anomalies in the system. The tool is mainly used to detect “correctness” problems. The author combines logs and source to extract three different signals: “message types”, “state variables”, and “message identifiers”. Based on these signals, they create two matrices: one matrix has “state variables” as the column, and time as the row, the other matrix uses “message types” as the column, and “message identifiers” as the row. Finally, PCA is used for anomaly detection. They perform PCA on the two matrices to get a reduced set of dimensions (eigenvectors) ranked by how much variance in the data each reduced dimension explains. Anomalous rows are identified by flagging those rows whose data is largely unexplained by the first K eigenvectors, which describes 95\% of the overall observed variance. 
After finding the anomalous rows, human need to manually interpret and further digging the root causes. In \cite{xu2010}, they further applied their algorithms into some of Google’s production logs. Since the data is large which makes it unrealistic to perform PCA, they used frequent mining techniques to segment the long-lasting sequence into sessions.

@@

\subsection{Models}
\label{sec:method:models}
We will begin by using two existing correlation-based models on our dataset. One is SPIRIT, an incremental PCA approach that adapts the number of hidden variables \cite{Papdimitriou2005}. The datasets we consider are significantly less periodic and more bursty than the ones explored in the SPIRIT paper, and we may need to adjust the approach accordingly.

@@

\section{Plan of Work}
\begin{tabular}{lll}
\bf Member & \bf Project Portion & \bf Papers Read \\
Yoshihisa Abe & & \cite{Zhu2002}, \cite{Zhu2003}, \cite{Sakurai2011} \\
Ilari Shafer & IPCA application/extension, scalability & \cite{Li2009}, \cite{Gmach2007}, \cite{Lavrenko2000} \\
Kai Ren & Data Collection + Preparation, Anomaly Detection Experiment &  \cite{xu2009}, \cite{xu2010}, \cite{nguyen2011} \\
Vishnu Boddeti & Kalman Filter Models & \cite{papadimitriou2005streaming}, \cite{roweis1999unifying}
\end{tabular}

@@

\bibliography{christosref,other}
\bibliographystyle{plain}
\newpage
\pagenumbering{roman}

>>>>

SPIRIT \cite{Papadimitriou2005} is an algorithm for discovering patterns in multiple streams of time-series data. This algorithm effectively tries to find correlations between the different data streams by performing principal component analysis on the the data covariance matrix. These principal components are modified and updated as each data sample is received at each time step while forgetting the samples. An interesting aspect of this algorithm is, anomaly detection which is done by detecting the changes in the number of principal components required to capture most of the energy in the signal.
In \cite{Roweis1999} the authors describe a unifying model for Linear Gaussian Models which includes PCA, Kalman Filters, Gaussian Mixture Models, ICA etc. They describe a general linear state transition model along with a linear observation model corrupted by independent Gaussian noise. They describe general algorithms to do inference and also learn the parameters of the model.

@@

Another console logs mining paper \cite{xu2009} extracts specific features from unstructured logs of Hadoop system \cite{ApacheSoftwareFoundation2011} (A distributed system for data intensive computing) and use them to detect anomalies in the system. The tool is mainly used to detect “correctness” problems. The author combines logs and source to extract three different signals: “message types”, “state variables”, and “message identifiers”. Based on these signals, they create two matrices: one matrix has “state variables” as the column, and time as the row, the other matrix uses “message types” as the column, and “message identifiers” as the row. Finally, PCA is used for anomaly detection. They perform PCA on the two matrices to get a reduced set of dimensions (eigenvectors) ranked by how much variance in the data each reduced dimension explains. Anomalous rows are identified by flagging those rows whose data is largely unexplained by the first K eigenvectors, which describes 95\% of the overall observed variance. 
After finding the anomalous rows, human need to manually interpret and further digging the root causes. In \cite{Xu}, they further applied their algorithms into some of Google’s production logs. Since the data is large which makes it unrealistic to perform PCA, they used frequent mining techniques to segment the long-lasting sequence into sessions.

@@

\subsection{Models}
\label{sec:method:models}
We will begin by using two existing correlation-based models on our dataset. One is SPIRIT, an incremental PCA approach that adapts the number of hidden variables \cite{Papadimitriou2005}. The datasets we consider are significantly less periodic and more bursty than the ones explored in the SPIRIT paper, and we may need to adjust the approach accordingly.

@@

\section{Plan of Work}
\begin{tabular}{lll}
\bf Member & \bf Project Portion & \bf Papers Read \\
Yoshihisa Abe & & \cite{Zhu2002}, \cite{Zhu2003}, \cite{Sakurai2011} \\
Ilari Shafer & IPCA application/extension, scalability & \cite{Li2009}, \cite{Gmach2007}, \cite{Lavrenko2000} \\
Kai Ren & Data Collection + Preparation, Anomaly Detection Experiment &  \cite{xu2009}, \cite{Xu}, \cite{nguyen2011} \\
Vishnu Boddeti & Kalman Filter Models & \cite{Papadimitriou2005}, \cite{Roweis1999}
\end{tabular}

@@

\bibliography{proposal}
\bibliographystyle{plain}
\newpage
\pagenumbering{roman}
